### 2014-10-16 tex/abstract.tex
Added Neha's changes to abstract

A fundamental challenge of using symbolic execution for software
analysis has been the treatment of dynamically allocated data.
State-of-the-art techniques have addressed this challenge
through the use of heap summaries and by constructing the concrete
heap ``lazily.'' In this work, we present a novel heap analysis technique
which takes inspiration from both approaches and builds exact heap summaries
lazily during symbolic execution. Our technique enables
exact analysis of program properties and
analysis of arbitrary recursive data structures. It also supports
dynamic bounds for linked data structure inputs, and
efficient sub-division of the underlying constraint problem.
We demonstrate the precision and scalability of our approach
in the Symbolic PathFinder framework for analyzing Java programs.

>>>>

A fundamental challenge of using symbolic execution for software
analysis has been the treatment of dynamically allocated data.
State-of-the-art techniques have addressed this challenge through
either (a) the use of summaries that over-approximate possible heaps, or
(b) by materializing a concrete heap lazily during generalized
symbolic execution. In this work, we present a novel heap
initialization and analysis technique which takes inspiration from
both approaches and constructs precise heap summaries lazily during
symbolic execution.  Our approach is 1) \emph{scalable}: it reduces the
points of non-determinism compared to generalized symbolic execution
and explores each control-flow path only once for any given set of
isomorphic heaps, 2) \emph{precise}: at any given point during symbolic
execution, the symbolic heap represents the exact set of feasible
concrete heap structures for the program under analysis, and 3)
\emph{expressive}: the symbolic heap can represent recursive data
structures. We demonstrate the precision and scalability of our
approach by implementing it as an extension to the Symbolic PathFinder
framework for analyzing Java programs.
